### 2018-09-19 ApproxComp/TKDE/sec-data.tex

The shortest path $\path(s, t)$ = $\path(s, u_s)/$ $\path(u_s, u_t)/$ $\path(u_t, t)$, where $u_s$ and $u_t$ are the proxies of $s$ and $t$, respectively.
Here  $\path(s, u_s)$ and $\path(u_t, t)$ are pre-computed, and $\path(u_s, u_t)$ can be computed on the reduced subgraph $G'$ by invoking any existing algorithms
(\eg \ah~\cite{zhu2013shortest}).
%
The shortest distance $\dist(s, t)$ = $\dist(s, u_s)$ + $\dist(u_s, u_t)$ + $\dist(u_t, t)$ can be computed along the same line.

@@

\stitle{(2) Network Anomaly Detection~\cite{HuAMH16}???}
Anomaly (or outlier) detection aims at identifying those objects in a database that are unusual, i.e., different than the majority of the data and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}. Network anomaly detection has become very popular
in recent years because of the importance of discovering key
regions of structural inconsistency in the network. In addition
to application-specific information carried by anomalies, the
presence of such structural inconsistency is often an impediment
to the effective application of data mining algorithms such as
community detection and classification.

@@

We have adopted the idea in the process of dealing with large graphs in the study of anomaly detection in graph streams, when dealing with the matrix representation of a social graph, and  we have both theoretically and experimentally shown that simplifying the matrix by replacing a part of small entry values  with zero has few affects on the computation of eigenvectors~\cite{YuAMW13}.

>>>>

The shortest path $\path(s, t)$ = $\path(s, u_s)/$ $\path(u_s, u_t)/$ $\path(u_t, t)$, where $u_s$ and $u_t$ are the proxies of $s$ and $t$, respectively.
As  $\path(s, u_s)$ and $\path(u_t, t)$ are pre-computed, and $\path(u_s, u_t)$ can be computed on the reduced subgraph $G'$ by invoking any existing algorithms
(\eg \ah~\cite{zhu2013shortest}).
%
The shortest distance $\dist(s, t)$ = $\dist(s, u_s)$ + $\dist(u_s, u_t)$ + $\dist(u_t, t)$ can be computed along the same line.

@@

\stitle{(2) Network Anomaly Detection~\cite{HuAMH16}}
Anomaly (or outlier) detection aims at identifying those objects in a database that are unusual, i.e., different than the majority of the data and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}. Network anomaly detection has become very popular
in recent years because of the importance of discovering key
regions of structural inconsistency in the network. In addition
to application-specific information carried by anomalies, the
presence of such structural inconsistency is often an impediment
to the effective application of data mining algorithms such as
community detection and classification.

@@

While a variety of graph embeddings, such as multidimensional scaling~\cite{mds}, are available in the literature, they aim to preserve (global) pairwise similarities and are not optimized to networks and the problem of anomaly detection.
Hence, they cannot be directly used for the detection of structural inconsistencies proposed in this paper. Therefore, a novel embedding method will be developed, which is specifically designed to ferret out the anomalous nodes in large networks.

The embedding approach is  based on a model,
in which each dimension of the embedding corresponds to a clustered
region in the network.
In other words, the similarity of different nodes along a particular dimension, indicates their similarity to a particular clustered region.
Therefore, this embedding retains
a very high level of interpretability in  terms of the original
graph data, which is very useful from an application-specific perspective.
The nature of  the embedding also  makes it  possible  to detect anomalous nodes, by examining the interaction of each node with the different regions in terms of the embedding.
In particular, we measure the {\em level of anomalousness} of a node in terms of the embedding imposed on the node and its neighbors.

Such an approach is however rather hard to apply to the case of large networks, because
the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and
because the noises in the embedding seriously impair the accuracy of detected anomalous nodes.
Hence, we incorporate the sampling and  graph partitioning techniques, and, moreover, propose a novel dimension reduction technique to make the approach more scalable and effective for large networks.

Using both real-life data and synthetic
data , we conduct an extensive experimental study.
We find that our embedding approach to network anomaly detection is both effective and efficient. (a) The modularity \cite{newman1} was increased about 2.9\% and 2.4\% for amazon, 4.9\% and 4.2\% for dblp and 6.3\% and 4.2\% for with our approach and oddball~\cite{akoglu14}, respectively; (b) The $F_1$ measure was about $88\%$ and $70\%$ for synthetic with our approach and oddball, respectively; And (c) the running time of our embedding approach increases reasonably with the increase of graph sizes, even with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.

### 2018-09-19 ApproxComp/TKDE/sec-query.tex

The rationale behind query approximation lies in that inexact or approximate answers are sufficient or acceptable for many big data analytic tasks.
On one hand, when the volume of data is extremely large, it may be impossible or not necessary to compute the exact answers.
Observe that nobody would try each and every store to find a pair of shoes with the best cost-performance ratio.
That is, inexact (approximate) solutions are good enough in this case.
%
On the other hand, when taking noises (common for big data) into account, it may not always be a good idea to compute exact answers
for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss possible candidates.

@@

\begin{figure}[tb!]
  \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.4]{./queryApprox.png}
  \end{center}
  \vspace{-4ex}
  \caption{Query approximation}\label{fig-tech-queryappro}
  \vspace{-4ex}
\end{figure}

\stitle{(1) Strong Simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
{\em graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg biology and social networks.

@@

The goodness of subgraph isomorphism is that all matched subgraphs  are exactly the same as the pattern graph, \ie completely preserving the  topology structure between the pattern graph and data graph. However, subgraph isomorphism is \NP-complete, and may return exponential many matched subgraphs.
Further, subgraph isomorphism is too restrictive to find sensible matches in certain scenarios, as observed in~\cite{FanLMTWW10}. Even worse, online data in many cases only represents a partial world (\eg terrorist collaboration networks and homosexual networks often involve with a large amount of off-line data).
Exact computations on such online data, whose accompanying off-line data is extremely hard to gather, typically decreases the chance of identifying candidate answers.
These hinder the usability of graph pattern matching in emerging applications.

@@

To rectify these problems, strong simulation, an ``approximate'' substitute for subgraph isomorphism, is proposed for graph pattern matching~\cite{tods-MaCFHW14}, such that strong simulation (a) theoretically preserves the key topology of pattern graphs and finds a bounded number of matches, (b) retains the same complexity as earlier extensions of graph simulation~\cite{FanLMTWW10,FanLMTW11}, by providing a cubic-time algorithm for computing strong simulation, and (c) has the locality property that allows us to develop an effective distributed algorithm to conduct graph pattern matching on distributed graphs.

@@

Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a subset of the former), such that the maximum distance of the former from the later is bounded by a user specified constant. It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.

>>>>

The rationale behind query approximation lies in that inexact or approximate answers are sufficient or acceptable for many big data analytic tasks.
On one hand, when the volume of data is extremely large, it may be impossible or not necessary to compute the exact answers.
Observe that nobody would try each and every store to find a pair of shoes with the best cost-performance ratio.
That is, inexact (approximate) solutions are good enough for certain cases.
%
On the other hand, when taking noises (very common for big data) into account, it may not always be a good idea to compute exact answers
for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss/ignore possible candidates.

@@

\begin{figure}[tb!]
 % \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.45]{./queryApprox.png}
  %\vspace{-1ex}
  \caption{Query approximation}\label{fig-tech-queryappro}
  \end{center}
  \vspace{-1ex}
\end{figure}

\stitle{(1) Strong Simulation~\cite{ShuaiMaVLDB12,tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
{\em graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg biology and social networks.

@@

The goodness of subgraph isomorphism is that all matched subgraphs  are exactly the same as the pattern graph, \ie completely preserving the  topology structure between the pattern graph and data graph. However, subgraph isomorphism is \NP-complete, and may return exponential many matched subgraphs.
Further, subgraph isomorphism is too restrictive to find sensible matches in certain scenarios, as observed in~\cite{FanLMTWW10}. Even worse, online data in many cases only represents a partial world (\eg terrorist collaboration networks and homosexual networks often involve with a large amount of off-line data).
Exact computations on such online data, whose off-line counterpart is extremely hard to gather, typically decreases the chance of identifying candidate answers.
These hinder the usability of graph pattern matching in emerging applications.

@@

To rectify these problems, strong simulation, an ``approximate'' substitute for subgraph isomorphism, is proposed for graph pattern matching~\cite{tods-MaCFHW14}, which (a) theoretically preserves the key topology of pattern graphs and finds a bounded number of matches, (b) retains the same complexity as earlier extensions of graph simulation~\cite{FanLMTWW10,FanLMTW11}, by providing a cubic-time algorithm for strong simulation compuation, and (c) has the locality property that allows us to develop an effective distributed algorithm to conduct graph pattern matching on distributed graphs.

@@

Piece-wise line simplification (\lsa) comes from the computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a subset of the former), such that the maximum distance of the former from the later is bounded by a user specified constant (\ie error bound). It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.
